{
% add braces so that commands defined for convenience are restricted locally to this file only

\subsection{Product manifold and quotient manifold by group action}

% coordinate map for convenience
\newcommand*{\x}{\mathbf{x}}
\newcommand*{\y}{\mathbf{y}}
\newcommand*{\z}{\mathbf{z}}
% isomorphism (category as input)
\newcommand*{\iso}[1]{\stackrel{\mathrm{#1.}}{\cong}}

\begin{proof}
\begin{enumerate}[(a)]
	\item
	Clearly, $M \times N$ is Hausdorff and second countable, and $\{U_\alpha \times V_\beta\}$ covers $M \times N$, with $\z_{\alpha,\beta}=(\x_\alpha,\y_\beta)$ being homeomorphic.
	\par
	Next, we shall show that the atlas is differentiable. Fix $(U_{\alpha_i} \times V_{\beta_i}, \z_{\alpha_i,\beta_i}) =: (W_i,\phi_i)$, where $i=1,2$, such that $O := \cap_{i=1}^2 \phi_i(W_i) \ne \emptyset$. Then the map
	\[\phi_2^{-1} \circ \phi_1: \phi_1^{-1}(O) \ni (p,q) \mapsto \left(\x_{\alpha_2}^{-1} \circ \x_{\alpha_1}(p), \y_{\beta_2}^{-1} \circ \y_{\beta_1}(q)\right) \in \phi_2^{-1}(O), p\in\mathbb{R}^{\mathrm{dim }M}, q\in\mathbb{R}^{\mathrm{dim }N}\]
	is clearly differentiable, by definition of $\{(U_\alpha,\x_\alpha)\}$ and $\{(V_\beta,\y_\beta)\}$ being differentiable structures on $M$ and $N$, respectively. Hence by definition, $\{U_\alpha \times V_\beta\}$ is a differentiable atlas on $M \times N$, and thus induces a unique differentiable structure on $M \times N$ (note that $\{(U_\alpha \times V_\beta,\z_{\alpha,\beta})\}$ is not maximal). So $M \times N$ equipped with the given atlas above is a differentiable manifold.
	\par
	Finally, we shall show that the projection onto $M$, 
	\[\pi_1: M \times N \ni (x,y) \mapsto x \in M, x \in M, y \in N,\]
	is differentiable. Fix $(x,y) \in M \times N$, and take, for convenience, $(U_\alpha, \x_\alpha)$ and $(V_\beta, \y_\beta)$ as the charts, with $p:= \x_\alpha^{-1}(x) \in U_\alpha$ and $q:= \y_\beta^{-1}(y) \in V_\beta$. Then the local expression of $\pi_1$ in the chosen charts is 
	\[ \left[x_\alpha^{-1} \circ \pi_1 \circ (x_\alpha, y_\beta)\right](p,q) = x_\alpha^{-1}[\pi_1(x,y)] = x_\alpha^{-1}(x) = p,\]
	which is obviously differentiable. Thus $\pi_1 \in C^\infty(M \times N; M)$.	By symmetry, the projection onto $N$, $\pi_2$, is also differentiable.
	
	\item
	We shall prove a slightly more general result: $\prod_{n=1}^N (M_n/G_n) \iso{diff} \left(\prod_{n=1}^N M_n\right)/\left(\prod_{n=1}^N G_n\right)$, where each group $G_n$ is a properly discontinuous action on the differentiable manifold $M_n$. In view of Example 4.8 and Part (a), $\prod_{n=1}^N (M_n/G_n)$ and $M:= \prod_{n=1}^N M_n$ are differentiable manifolds with the associated product differentiable structures. We shall show that $G:= \prod_{n=1}^N G_n$ acts on $M$ properly discontinuously and that the associated quotient differentiable structure coincides with the product differentiable structure of $\prod_{n=1}^N (M_n/G_n)$.
	\par
	As a corollary, $\left(S^1\right)^n \iso{diff} T^n$ follows from the fact that $S^1 \iso{diff} \mathbb{R}/\mathbb{Z} \iso{diff} T^1$.
	\par
	We first check that $G$ is a properly discontinuous group action on $M$. Fix $g_n \in G_n$ for every $n$, since $M_n \ni p_n \mapsto g_n p_n \in M_n$ is a diffeomorphic automorphism on $M_n$,
	\[ M \ni p:= (p_1,\dots,p_N) \mapsto (g_1 p_1, \dots, g_N p_N) =:g p \in M, p_n \in M_n \]
	is also a diffeomorphic automorphism on $M$. Now fix $p_n \in M_n$, by proper discontinuity of $G_n$ on $M_n$, we can find an open subset of $M_n$, $U_n \in p_n$, so as ${U_n \cap g_n(U_n) = \emptyset}, { \forall g_n \in G_n\backslash\{e_n\} }$. Note that $V:=\prod_{n=1}^{N} U_n$ is and open neighborhood of $p \in M$, and that
	\[V \cap g(V) = \left[\prod_{n=1}^N U_n \right] \cap \left[\prod_{n=1}^N g_n(U_n) \right] = \prod_{n=1}^N \left[U_n \cap g_n(U_n)\right] = \emptyset, \forall g \in G\backslash\{e\}.\]
	So $G$ is a properly discontinuous action on $M$.
	\par
	Now we shall show that the product differentiable structure is the same as the quotient differentiable structure, which means finding a diffeomorphism $\phi: M/G \rightarrow \prod_{n=1}^N (M_n/G_n)$, and this completes the proof. For each $n$, let $\{(O_n^{\alpha_n}, \x_n^{\alpha_n})\}$ be a differentiable atlas on $M_n$ with	$ \x_n^{\alpha_n}(O_n^{\alpha_n}) \cap g_n\left(\x_n^{\alpha_n}(O_n^{\alpha_n})\right) = \emptyset, \forall g_n \in G_n\backslash\{e_n\}, \alpha^n$, and ${ q_n: M_n \ni p_n \mapsto [p_n]_{G_n} \in M_n/G_n }$ be the quotient map (projection). Then we know from the construction of quotient manifold by group action, $\{(O_n^{\alpha_n}, \y_n^{\alpha_n}:= q_n \circ \x_n^{\alpha_n})\}$ induces the quotient differentiable structure on $M_n/G_n$. By Part (a), $\{(O^\alpha:= \prod_{n=1}^N O_n^{\alpha_n}, \y^\alpha:= (\y_1^{\alpha_1}, \dots, \y_N^{\alpha_N})\}$ gives a differentiable atlas on $\prod_{n=1}^N (M_n/G_n)$. Similarly, ${ \{(O^{\alpha}, \x^{\alpha}:= (\x_1^{\alpha_1}, \dots, \x_N^{\alpha_N})\} }$ is a differentiable atlas on $M$, and from the proof of proper discontinuity, ${ \x^\alpha(O^\alpha) \cap g\left(\x^\alpha(O^\alpha)\right) = \emptyset }, { \forall g \in G\backslash\{e\} }$. Hence, ${ \{O^\alpha, \z^\alpha:= q \circ \x^\alpha\} }$ determines the quotient differentiable structure on $M/G$, where ${ q:= (q_1, \dots, q_N) }$. Consider ${ \phi:M/G \ni [p]_G \mapsto ([p_1]_{G_1}, \dots, [p_N]_{G_N}) \in \prod_{n=1}^N M_n/G_n }$, which is obviously well-defined and bijective. For $[p]_G \in M/G$, let ${ (O^\alpha, \z^\alpha) }$ be such that ${ O^\alpha \ni z:=(\z^\alpha)^{-1}([p]_G) }$, Observe that 
	\[ \left( \y^\alpha \right)^{-1} \circ \phi \circ \z^\alpha (z) 
	= \left( \y^\alpha \right)^{-1} \left[ \phi \left([p]_G\right) \right]
	= \left( \y^\alpha \right)^{-1}\left(([p_1]_{G_1}, \dots, [p_N]_{G_N})\right)
	= (z_1, \dots, z_N) = z
	\]
	and hence ${ \phi \in C^\infty(M/G;\prod_{n=1}^N (M_n/G_n)) }$ as claimed. Thus, ${ \prod_{n=1}^N (M_n/G_n) \iso{diff} M/G }$ .
	
\end{enumerate}
\end{proof}

}